Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Uncomment comment, so that Markus can read it

%% \begin{quote}
%%     sol: We e.g. say ill-behaved Monoid instance.  So is
%%     ``behavior'' really a bad word?  But I agree that some people in
%%     the community might associated it with something imperative.

%%     One might also argue that ``should'' is not very mathematical, but
%%     it is common language when we talk about mathematics.  E.g. Brent
%%     Yorgey uses ``should'' a lot in the Typeclassopedia (e.g. ``\ldots
%%     {\tt Alternative} should satisfy the monoid laws\ldots'')
%% \end{quote}

>>>>

\begin{quote}
    sol: We e.g. say ill-behaved Monoid instance.  So is
    ``behavior'' really a bad word?  But I agree that some people in
    the community might associated it with something imperative.

    One might also argue that ``should'' is not very mathematical, but
    it is common language when we talk about mathematics.  E.g. Brent
    Yorgey uses ``should'' a lot in the Typeclassopedia (e.g. ``\ldots
    {\tt Alternative} should satisfy the monoid laws\ldots'')
\end{quote}
